Draft

### 2022-06-15 draft/draft.qmd
improved line spacing with correlation list
added introduction and references section

## Introduction

@@

In this project, we are researching the factors that influence Americans’ abortion attitudes. Specifically, we would like to know which demographic factors (such as age, gender, and education level) and personal attitudes towards other issues (such as political ideology, importance of religion, and respect for authority) best predict an individual’s attitude towards abortion. We will conduct our analysis using data collected about Americans’ abortion attitudes, demographic information, as well as attitudes about other issues. The data are a nationally representative sample of the American people; hence we can infer that all the observations are independent and the variables may show a linear relationship. Given that this issue has become highly polarized by political party, we predict that holding liberal political ideology and liberal attitudes on other issues, as well as being younger in age is correlated with believing that abortion is more justified. (the exact predictors we will use will be decided after model selection).

Works Cited

@@

>>>>

## Introduction and Research Question

@@

In this project, we are researching the factors that influence Americans’ abortion attitudes. Specifically, we would like to know which demographic factors (such as age, gender, and education level) and personal attitudes towards other issues (such as political ideology, importance of religion, and respect for authority) best predict an individual’s attitude towards abortion. We will conduct our analysis using data collected through the World Values Survey about Americans’ abortion attitudes, demographic information, as well as attitudes about other issues. The data are a nationally representative sample of the American people; hence we can infer that all the observations are independent and the variables may show a linear relationship. Given that this issue has become highly polarized by political party, we predict that holding liberal political ideology and liberal attitudes on other issues, as well as being younger in age is correlated with believing that abortion is more justified. (the exact predictors we will use will be decided after model selection).

@@

## References
